A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-13 manuscript.Rmd
use hash hash is incorrect, because simulation is running
cite worcs for synthethic data
forgot to clean up after removing preregistration.Rmd

---
title: "A Hitchhiker's Guide to Reproducible Research" # replace with something serious
author: Aaron Peikert and Andreas M. Brandmaier 
output: bookdown::pdf_document2
repro:
  packages:
    - tidyverse
    - usethis
    - gert
    - aaronpeikert/repro@7bfaf98
    - here
    - rstudio/webshot2@f62e743
    - targets
    - renv
    - slider
    - patchwork
    - knitr
  scripts:
    - R/simulation.R
    - R/simulation_funs.R
    - R/link.R
csl: apa7.csl
numbered_headings: true
bibliography: ["references.bib", "packages.bib"]
---

@@

@@

An compromise between making the data publicly available and keeping it closed is to publish synthetic data.
Such approach tries to recreate the marginal distribution and bivariate relationships in simulated data, e.g. with the R package `synthpop`[@nowokSynthpopBespokeCreation2016].
The results of such data should generally not be interpreted.
However, synthetic data provides an opportunity for readers to test if a project is in principle reproducible, even though they have no access to the data.

>>>>

---
title: "A Hitchhiker's Guide to Reproducible Research" # replace with something serious
author: Aaron Peikert and Andreas M. Brandmaier 
output: bookdown::pdf_document2
repro:
  packages:
    - tidyverse
    - usethis
    - gert
    - aaronpeikert/repro@7bfaf98
    - here
    - rstudio/webshot2@f62e743
    - targets
    - renv
    - slider
    - patchwork
    - knitr
    - pander
    - lavaan
    - furrr
    - future.batchtools
  scripts:
    - R/simulation.R
    - R/simulation_funs.R
    - R/link.R
csl: apa7.csl
numbered_headings: true
bibliography: ["references.bib", "packages.bib"]
---

@@

```{r hash}
```

@@

An compromise between making the data publicly available and keeping it closed is to publish synthetic data [@vanlissa2020worcs].
Such approach tries to recreate the marginal distribution and bivariate relationships in simulated data, e.g. with the R package `synthpop`[@nowokSynthpopBespokeCreation2016].
The results of such data should generally not be interpreted.
However, synthetic data provides an opportunity for readers to test if a project is in principle reproducible, even though they have no access to the data.
